Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-10 Supplemental-Material-B-Annotated-Analysis.Rmd
Update Supplemental-Material-B-Annotated-Analysis.Rmd

## Data Cleaning

@@

## Data Exclusions

>>>>

## Data Cleaning & Data Exclusions

@@

## Calculate needed transformations

```{r newVarsWorkers}
# ID variables
  short <- dtWorker$clean %>%
    mutate(
      PID = as.numeric(factor(ExternalReference)), # participant ID
      TID = measureID-1, # time ID with t0 = 0 for meaningfull intercept interpretations
      date = substr(StartDate,1,10), # awkward way of extracting date (best converted to )
      time = substr(StartDate,12,19), # awkward way of extracting time
      daynum = as.numeric(factor(date)), # all days as numeric for ordering
      daycor = ifelse(daytime=="morning" & period_to_seconds(hms(time))<period_to_seconds(hms("12:00:00")) | daytime=="afternoon" & period_to_seconds(hms(time))<period_to_seconds(hms("19:00:00")),daynum-1,daynum), # correctly identify which date the questionnaire is about
      daycor.lead = sprintf("%02d", daycor),
      daytime.lt = ifelse(daytime=="morning","a","b"), # morning / afternoon to a / b 
      day_time = paste(daycor.lead, daytime.lt, sep="_"), # combine day id with morning / afternoon
      session = as.numeric(factor(day_time)) # day and time identifier as numeric id
    )

  df <- dtWorker$clean

  df$PID = as.numeric(factor(df$ExternalReference)) # participant ID
  df$TID = df$measureID-1 # time ID with t0 = 0 for meaningful intercept interpretations

# Time and Date Variables: Correct morning / afternoon date where survey was collected the day after to indicate the correct date that was targeted
  df$SubTime = chron::times(df$time.0)
  df$SubTime[df$daytime == "afternoon"] = paste0(substring(as.character(df$time.0[df$daytime == "afternoon"]),4,8),":00")

  df$PPDate = as.Date(df$date.daily)
  df$PPDate[df$SubTime < "11:50:00" & df$daytime == "morning"] = df$PPDate[df$SubTime < "11:50:00" & df$daytime == "morning"]-1
  df$PPDate[df$SubTime < "18:50:00" & df$daytime == "afternoon"] = df$PPDate[df$SubTime < "18:50:00" & df$daytime == "afternoon"]-1

  df$time.daily = as.character(df$time.daily)
  df$time.daily[df$daytime == "afternoon" & !is.na(df$time.daily!="<NA>")] = paste0(substring(as.character(df$time.daily[df$daytime == "afternoon" & !is.na(df$time.daily!="<NA>")]),4,8),":00")

# Mood scales
  df$calmness.daily = rowSums(df[, c("calmness1", "calmness2")], na.rm = T)
  df$alertness.daily = rowSums(df[, c("alertness1", "alertness2")], na.rm =T)
  df$valence.daily = rowSums(df[, c("valence1", "valence2")], na.rm = T)

# Need scales
  df$keyMotiveFulfilled = rowSums(df[,c("keymotive_fulfillemt_1","keyMotive_noInt_fulf_1")], na.rm=T)
  df$autonomy.daily.all = rowSums(df[,c("autonomy_1","autonomy_NoInt_1")], na.rm=T)
  df$competence.daily.all = rowSums(df[,c("competence_1","competence_NoInt_1")], na.rm=T)
  #cor(df$relatedness_other_1, df$relatedness_self_1,use="complete.obs")
  df$relatedness.daily.all = rowMeans(df[,c("relatedness_other_1","relatedness_self_1","relatedness_1_NoInt_1")], na.rm=T)

# summarize by participant
  df$number[is.na(df$number)] = 0
  df$NonDutchNum[is.na(df$NonDutchNum)] = 0
  count = aggregate(list(CtContactNL=df$Contact_dum,
                         CtContactNonNl=df$inNonDutch,
                         CtContactNLAll=df$number,
                         CtContactNonNlAll=df$NonDutchNum), 
                    by=list(ExternalReference=df$ExternalReference), 
                    FUN=sum)
  average = aggregate(list(AvKeyNeed=df$keyMotiveFulfilled,
                           AvKeyNeedInt=df$keymotive_fulfillemt_1,
                           AvKeyNeedNoInt=df$keyMotive_noInt_fulf_1,
                           AvAutonomy=df$autonomy.daily.all,
                           AvCompetence=df$competence.daily.all,
                           AvRelatedness=df$relatedness.daily.all,
                           AvThermo=df$thermometerDutch_1,
                           AvWB=df$ExWB_1),
                      by=list(ExternalReference=df$ExternalReference), 
                      FUN=mean, na.rm=T)

  df.btw = df[,-c(9:162)]
  df.btw = df.btw[,-grep(names(df.btw),pattern="daily|ID|keyMotive")]

  df.btw = Reduce(function(x, y) merge(x, y, by="ExternalReference", all=TRUE), list(df.btw, count, average))
  df.btw = df.btw[!duplicated(df.btw$ExternalReference),]

  df.btw[!is.na(df.btw$assimilation.post),]

  df.btw$CtContactNL_c = scale(df.btw$CtContactNL, scale = FALSE)
  df.btw$AvKeyNeedInt_c = scale(df.btw$AvKeyNeedInt, scale = FALSE)
  df.btw$AvKeyNeed_c = scale(df.btw$AvKeyNeed, scale = FALSE)
  df.btw$CtContactNL_z = scale(df.btw$CtContactNL, scale = T)
  df.btw$AvKeyNeedInt_z = scale(df.btw$AvKeyNeedInt, scale = T)
  df.btw$AvKeyNeed_z = scale(df.btw$AvKeyNeed, scale = T)

  .GlobalEnv$df.btw = df.btw

  save(df.btw, file = "data/processed/df.btw.RData")  
  #write_sav(df.btw, "data/processed/MT_clean-merged_pre-post.sav")

# export data to Mplus

  df.mplus = remove_all_labels(select(df, PID, session, thermometerDutch_1, inNonDutch, Contact_dum, keyMotiveFulfilled, autonomy.daily.all, competence.daily.all, relatedness.daily.all))
  names(df.mplus)= c("PID", "session", "att", "intin", "intout", "keymot", "aut", "comp", "rel")
  mplus = df.mplus[order(df.mplus$PID, df.mplus$session),]
  mplus.intcont = mplus[mplus$intout==1,]
  prepareMplusData(mplus.intcont, "data/processed/dynamic-subset-intonly.dat")
